Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-18 doc/report/intro.tex
update intro (TBC)

The vision of smart-home and smart office is being realized recently with the development of radio technology, sensors, and actuators. Nowadays, you can buy the basic components online \cite{SmartHome, NinjaBlocks} and many hobbyists have already created their own smart environment (see \cite{BRAD} as an example). Though various challenges are ahead in the field to build a more robust, scalable, energy-efficient, and user-friendly systems, the general trend of having smart devices around us is undoubted. Those smart devices each can be controlled separately (like what is existing now for television and heater), however, with the prevalence of smartphones, many systems \cite{SmartThings, Lockitron} are being written as an application on mobile platforms so that the smartphone act as the bridge of connecting digital world and physical world.

>>>>

The vision of smart-home and smart office is being realized recently with the development of radio technology, sensors, and actuators. Nowadays, you can buy the basic components online \cite{SmartHome, NinjaBlocks} and many hobbyists have already created their own smart environment (see \cite{BRAD} as an example). Though various challenges are ahead in the field to build a more robust, scalable, energy-efficient, and user-friendly systems, the general trend of having smart appliances around us is foreseeable. Those smart appliances each can be controlled separately (like what is existing now for television and heater), however, with the prevalence of smartphones, many systems \cite{SmartThings, Lockitron} are being designed as applications on mobile platforms so that the smartphone act as an universal bridge between human and appliances.
